\bf Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2015-05-31 nips2015.tex
ENH: wrote about T-BD algorithm and proposed a new theorem

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e}%,times}
%\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmic}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}

@@

\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\prox}{Prox}

@@

\subsection{Statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{von1996efficient,vonequilibrium}, where it was established that
for sequential two-person zero-sum games with imcomplete information
and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1
  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
all linear in the size of the game tree (number of states in the game)
and such that Nash equilibria correspond to pairs $(x, y)$ of
\textit{realization plans} which solve the primal LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }p_0, \hspace{.5em}\text{ subject to }(y,p) \in
     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-q_0,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{duality gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}

@@

\section{Our contributions}
\label{sec:algo}
\subsection{Primal-dual algorithm}
It should be noted that the difficulty of applying the general
primal-dual Algorithm 39 proposed in \cite{chambolle2010} directly to
problem \eqref{eq:primal_pb} lies in the difficulty of effectively
computing the euclidean projections $\proj_{Q_k}$ (which are the
proximal operators here). Theorem \ref{thm:pd} provides a trick to
effectively evade this difficulty, by re-writting the problem into an
equivalent saddle-point convex-concave problem for which the
associated proximal operators are simple.

\begin{theorem}
  The Nash equilibrium LCPs \eqref{eq:primal_pb} and
  \eqref{eq:dual_pb} are equivalent to the following convex-concave
  saddle-point problems

  \begin{equation}
    \underset{y, p}{\text{minimize}}\text{ }\underset{x, q}{\text{maximize}}
           {\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix} + G_2(y, p) - G_2(x, q)}
           \label{eq:unconstrained_pb}
  \end{equation}

  where the $(n_1 + l_2)$-by-$(n_2 + l_1)$ matrix $K$ is defined by
  \begin{equation}
    K :=
    \left[
      \begin{array}{cc}
        A & -E_1^T \\
        E_2 & 0_{l_2, l_1}
      \end{array}
      \right]
\end{equation}

and the p.c.l.s.c functions $G_1: \mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow (-\infty, +\infty]$ and \\$G_2: \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ are defined by
  \begin{equation}
      G_1(y, p) := i_{\mathbb{R}^{n_2}_+}(y) + p_0, \hspace{1em} G_2(x, q) := i_{\mathbb{R}^{n_1}_+}(x) + q_0
    \label{eq:things}
  \end{equation}

  %% Moreover, if $\mathcal{G_1}'$ denotes the dual-gap function of problem $\eqref{eq:unconstrained_pb}$ and as before, $\mathcal{G_1}$ denotes the dual-gap function of problem \eqref{eq:primal_pb}, then we have the bound
  %% \begin{equation}
  %%   \mathcal{G_1}(x, y) \le \mathcal{G_1}'(x, u, y, v), \forall (x, u, y, v) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}
  %%   \end{equation}

  \label{thm:pd}
\end{theorem}

%% Theorem \ref{thm:pd}, can be interpreted as follows: 2 players $x$ (player 1)  and $y$ (player 2) go heads-on in a zero-sum game with payoff matrix $A$. Their strategy, profiles are $Q_1$ and $Q_2$ respectively, meaning that if player $j$ players a strategy which is outside $Q_k$ then they are panalized by inflicting an infinite loss yupon them. To remedy this, they recruit assistants $u$ and $v$, whose sole goal is to preven the ...
\begin{proof}
Define the following closed convex sets
\begin{eqnarray*}
  \begin{aligned}
  \Sigma_2 &:= \{(y, p) \in \mathbb{R}^{n_2} \times
  \mathbb{R}^{l_1}\text{ }|\text{ } -Ay + E_1^Tp \ge 0, E_2y = e_2, y
  \ge 0\}\\
  \Sigma_1 &:= \{(x, q) \in \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}\text{ }|\text{ } -A^Tx - E_2^Tq \le 0, E_1x = e_1,
  x \ge 0\}
  \end{aligned}
\end{eqnarray*}
The optimal value in the dual LCP \eqref{eq:primal_pb} can be computed as 
\begin{eqnarray*}
  \begin{aligned}
    p_0^* &= \text{min}\{p_0\text{ }|\text{ } (y, p) \in \Sigma_2, p =
    (p_0, p_1, ..., q_{l_1-1})\}\\
    &= \underset{y,p}{\text{min}}\text{ }p_0 +
    i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
    i_{\{0\}}(E_2y - e_2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
    i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x \geq
      0}{\text{max}}\text{ }x^T(Ay - E_1^Tp) +
    \underset{q}{\text{max}}\text{ }q^T(E_2y - e_2)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,
      q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y -
    i_{\mathbb{R}^{n_1}_+}(x) - q^Te_2\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) + \underset{x,
      q}{\text{max}}\text{ }x^TAy - x^TE_1^Tp + q^TE_2y -
    (i_{\mathbb{R}^{n_1}_+}(x) + q_0)\\
    &= \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
    \underset{x,q}{\text{max}}\text{
    }\begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}
      - G_2(x, q) = \underset{y,p}{\text{min}}\text{ }G_1(y,p) +
      G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}
Thus the LCP \eqref{eq:primal_pb} can be written as 
\begin{equation}
  \underset{y,p}{\text{minimize}}\text{ }G_1(y,p) +
  G_2^*\left(K\begin{bmatrix}y\\p\end{bmatrix}\right)
\end{equation}
Similarly, the optimal value in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 -q_0^* &= \text{max}\{-q_0\text{ }|\text{ } (x, q) \in \Sigma_1, q =
 (q_0, q_1, ..., q_{l_2-1})\}\\
    &= \underset{x,q}{\text{max}}\text{ }-q_0 -
 i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(E_1x - e_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q) - \underset{y \geq
   0}{\text{max}}\text{ }y^T(-A^Tx - E_2^Tq) -
 \underset{p}{\text{max}}\text{ }p^T(E_1x-e_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x, q)
 -\underset{y,p}{\text{max}}\text{ }-(y^TA^Tx -p^TE_1x +
 y^TE_2^Tq)-(i_{\mathbb{R}^{n_2}_+}(y) + p^Te_1)\\
    &= \underset{x,q}{\text{max}}\text{ }-G_2(x,
 q)-\underset{y,p}{\text{max}}\text{ }-
 \begin{bmatrix}y\\p\end{bmatrix}K^T\begin{bmatrix}x\\q\end{bmatrix}-G_1(y,p)
   = \underset{x,q}{\text{max}}\text{ }-G_2(x,
   q)-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right),
  \end{aligned}
\end{eqnarray*}
and so the the LCP \eqref{eq:dual_pb} is equivalent to
\begin{equation}
  \underset{x,q}{\text{maximize}}\text{
  }-G_1^*\left(-K^T\begin{bmatrix}x\\q\end{bmatrix}\right) - G_2(x, q)
\end{equation}
But these last two equations are simply the primal and dual
formulations respectively, of the saddle-point problem
\eqref{eq:unconstrained_pb}, and we are done.

%% For the dual-gap bound, note that $\forall (x', u', y', v') \in \mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$, one has
%% \begin{eqnarray*}
%%   \begin{split}
%%     \underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{max}\text{ }\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y'\\v'\end{bmatrix} + G_1(y', v') - G_2(x, u)
%%       &= \underset{x \in \mathbb{R}^{n_1}_+, u \in \mathbb{R}^{l_2}}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + u^T(E_2y' - e_2)\\
%%       &\ge \underset{x \in \mathbb{R}^{n_1}_+}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + \underset{u \in \mathbb{R}^{l_2}}{max}\text{ }u^T(E_2y' - e_2)\\
%%       &\ge \underset{x \in Q_1}{max}\text{ }x^TAy + \underset{u \in \mathbb{R}^{l_2}}{max}\text{ }u^T(E_2y' - e_2)
%%   \end{split}
%% \end{eqnarray*}

%% and
%% \begin{eqnarray*}
%%   \begin{split}
%%     \underset{y \in \mathbb{R}^{n_2}, v \in \mathbb{R}^{l_1}}{min}\text{ }\begin{bmatrix}x'\\u'\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + G_1(y, v) - G_2(x', u')
%%       &= \underset{y \in \mathbb{R}^{n_2}_+, v \in \mathbb{R}^{l_1}}{min}\text{ }x'^TAy - v^T(E_1x' - e_1) + u'^T(E_2y - e_2)\\
%%       &\le \underset{y \in \mathbb{R}^{n_2}_+}{min}\text{ }x'^TAy + u'^T(E_2y - e_2) - v^T(E_1x' - e_1)
%%   \end{split}
%% \end{eqnarray*}
\end{proof}

@@

\paragraph{In summary.}
According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
\eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
saddle-point problem \eqref{eq:unconstrained_pb}.
In order to apply Algorithm 39 of \cite{chambolle2010}, we need
formulae for the proximal operators of
$G_1$ and $G_2$. Now, either of $G_1$ and $G_2$ is a separable sum of
the indicator function of a convex set, whose prox is simply the
euclidean projection onto the set,  and a linear transformation $z
\mapsto a^Tz$ whose prox is simply $z \mapsto z - \tau a$. Thus,  one
computes their respective proximal operators $\prox_{\tau G_1} :
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \rightarrow \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1}$, $\prox_{\sigma G_2}: \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}$
as

  \begin{equation}
    \prox_{\tau G_1}(y, p) = ((y)_+, p - \tau e_1), \hspace{1em}
    \prox_{\sigma G_2}(x, q) = ((x)_+, q - \sigma e_2)
  \end{equation}

Finally, applying Algorithm 39 of \cite{chambolle2010} to problem \eqref{eq:unconstrained_pb} we obtain Algorithm \ref{Tab:algo_simplified}. Its $\mathcal{O}(1/\epsilon)$ convergence rate in terms of the duality gap is immediate. Indeed,
%% \subsection{Special case: $C_k = \mathbb{R}^{n_k}_+$} As discussed in subsection \ref{subsec:example_games},
%% the Nash equilibrium problem for two-person zero-sum simultaneous games and two-person zero-sum sequential games with imcomplete
%% information and perfect recall admits the formulation \eqref{eq:primal_pb}, with $C_k = \mathbb{R}^{n_k}_+$ (coding for nonnegativity constraints).
%% In such situations, $\proj_{C_k}(z) \equiv (z)_+$ as already mentioned in \ref{sec:notation}, and Algorithm \ref{Tab:algo} reduces to the simpler Algorithm \ref{Tab:algo_simplified}.

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e,times}
%\usepackage{hyperref}
\usepackage{url}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}

\usepackage{algpseudocode}
\usepackage{pifont}

@@

\DeclareMathOperator{\dom}{dom}
\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\prox}{prox}

@@

\subsection{Statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{von1996efficient,vonequilibrium}, where it was established that
for sequential two-person zero-sum games with imcomplete information
and perfect recall, there exist sparse matrices $A \in \mathbb{R}^{n_1
  \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times n_1}$, $E_2 \in
\mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in \mathbb{R}^{l_1},
e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$, $l_1$, and $l_2$ are
all linear in the size of the game tree (number of states in the game)
and such that Nash equilibria correspond to pairs $(x, y)$ of
\textit{realization plans} which solve the primal LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }e_1^Tp, \hspace{.5em}\text{ subject to }(y,p) \in
     \mathbb{R}^{n_2} \times \mathbb{R}^{l_1}, -Ay +
    E_1^Tp \geq 0, E_2y = e_2, y \ge 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-e_2^Tq,\hspace{.5em}\text{subject to }(y,q) \in
    \mathbb{R}^{n_1} \times \mathbb{R}^{l_2}, -A^Tx - E_2^Tq \leq 0,
    E_1x = e_1, x \ge 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$[1, 0, ..., 0]$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^n_+ |\text{ }E_kz = e_k\}
\label{eq:polyhedron}
\end{equation}
Note that $p^Te_1 = p_0$ and $q^Te_2 = q_0$ by definition of $e_1$ and
$e_2$. At a feasible point $(y, p, x, q)$, the \textit{duality gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := p_0 - (-q_0) = p_0 + q_0
  \label{eq:dgap}
\end{equation}

@@

\section{Our contributions}
\label{sec:algo}
\subsection{Reformulation as a Generalized Saddle-point Problem (GSP)}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item avoid having to compute the projections $\proj_{Q_k}$, and
\item cope  with infinite primal-dual gaps.
\end{itemize}

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{\mathbb{R}^{n_2}_+}(y) + e_1^Tp\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{\mathbb{R}^{n_1}_+}(x) + e_2^Tq.
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

Also, define two bilinear forms $\Psi_1$, $\Psi_2: \mathbb{R}^{n_2}
\times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
\mathbb{R}^{l_2} \rightarrow \mathbb{R}$ by letting
  \begin{equation}
      K :=
      \left[
        \begin{array}{cc}
          A & -E_1^T \\
          E_2 & 0_{l_2, l_1}
        \end{array}
        \right],\hspace{.5em}
    \Psi_1(y, p, x, q)
    := \begin{bmatrix}x\\q\end{bmatrix}^TK\begin{bmatrix}y\\p\end{bmatrix}, \hspace{.5em}
      \Psi_2(y, p, x, q) := -\Psi_1(y, p, x, q).
\end{equation}

Finally, define the functions $\hat{\Psi}_1$, $\hat{\Psi}_2:
\mathbb{R}^{n_2} \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}
\times \mathbb{R}^{l_2} \rightarrow (-\infty, +\infty]$ by
\begin{eqnarray}
  \left.
  \begin{aligned}
    \hat{\Psi}_1(y, p, x, q) &:=
    \Psi_1(y, p, x, q)+ g_1(y, p) \text{ if }y \ge 0, \hat{\Psi}_1(y,
    p, x, q) := \infty \text{ otherwise}\\
    \hat{\Psi}_2(y, p, x, q) &:= \Psi_2(y, p, x, q)+ g_2(y, p) \text{ if
    }x \ge 0, \hat{\Psi}_2(y,p, x, q) := \infty \text{ otherwise}.
  \end{aligned}
  \right\}
\end{eqnarray}

Consider the GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$)
  \begin{eqnarray}
    \left.
    \begin{aligned}
      \text{Find }(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}_+
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
  \mathbb{R}^{l_2}\text{ such that }\hat{\Psi}_1(y^*, p^*, x^*, q^*) \le \hat{\Psi}_1(y, p, x^*, q^*)
      \text{ and }\\
      \hspace{.5em}\hat{\Psi}_2(y^*, p^*, x^*, q^*) \le
      \hat{\Psi}_2(y^*, p^*, x, q)
        \forall (y,p, x, q) \in \mathbb{R}^{n_2}_+
      \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1}_+ \times
      \mathbb{R}^{l_2}.
    \end{aligned}
    \right\}
    \label{eq:unconstrained_pb}
  \end{eqnarray}
  \label{thm:pd}

  Then a quadruplet $(y^*,p^*, x^*, q^*) \in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$ solves the Nash equilibrium LCPs
  \eqref{eq:primal_pb} and \eqref{eq:dual_pb} iff it solves
  GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).
  \label{thm:pd}
\end{theorem}

\begin{proof}
Define $S_1 := \dom(g_1) = \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$
and $S_2 := \dom(g_2) = 
\mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2}$. Noting that the
equilibria of the LCPs \eqref{eq:primal_pb},
\eqref{eq:dual_pb}, and the equilibria of GSP($\Psi_1$, $\Psi_2$,
$g_1$, $g_2$) are contained in $S_1 \times S_2$, it suffices to show
that at any point $(y, p, x, q) \in S_1 \times S_2$, the duality
primal-dual gap between the primal LCP \eqref{eq:primal_pb} and the
dual LCP \eqref{eq:dual_pb} equals the primal-dual gap of
GSP($\Psi_1$, $\Psi_2$, $g_1$, $g_2$).

Indeed, the unconstrained objective in \eqref{eq:primal_pb}, say
$a(x,y)$, can be written as
\begin{eqnarray*}
  \begin{aligned}
    a(y,p) &= e_1^Tp +
    i_{\mathbb{R}^{n_2}_+}(y) + i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) +
    i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) +
    i_{\mathbb{R}^{n_1}_+}(-Ay + E_1^Tp) + i_{\{0\}}(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x' \geq
      0}{\text{max}}\text{ }x'^T(Ay - E_1^Tp) +
    \underset{q'}{\text{max}}\text{ }q'^T(E_2y - e_2)\\
    &= g_1(y,p) + \underset{x',
      q'}{\text{max}}\text{ }x'^TAy - x^TE_1^Tp + q'^TE_2y -
    (i_{\mathbb{R}^{n_1}_+}(x') + e_2^Tq)\\
    &= g_1(y,p)
      - \underset{x',q'}{\text{min}}\text{ }\Psi_2(y, p, x', q') + g_2(x',
      q') = g_1(y,p) -\phi_2(y,p),
  \end{aligned}
  \label{eq:a}
\end{eqnarray*}

where $\phi_2(y, p) := \underset{x',q'}{\text{min}}\text{
}\hat{\Psi}_2(y, p, x', q') \in [-\infty, +\infty)$.
Similarly, the unconstrained objective, say
$b(x, q)$, in the dual LCP \eqref{eq:dual_pb} writes
\begin{eqnarray*}
  \begin{aligned}
 b(x, q) &= 
 -i_{\mathbb{R}^{n_1}_+}(x) - i_{\mathbb{R}^{n_2}_+}(A^Tx+E_2^Tq) -
 i_{\{0\}}(e_1 - E_1x)\\
    &= -g_2(x, q) + \underset{y' \geq
   0}{\text{min}}\text{ }y'^T(A^Tx + E_2^Tq) +
 \underset{p'}{\text{min}}\text{ }p'^T(e_1-E_1x)\\
    &= -g_2(x, q)
 +\underset{y',p'}{\text{max}}\text{ }\Psi_1(y', p', x, q) +
 g_1(y', p') = -g_2(x, q) + \phi_1(x, q),
   \end{aligned}
\end{eqnarray*}
where $\phi_1(x, q) :=
\underset{y',p'}{\text{min}}\text{ }\hat{\Psi}_1(y', p', x, q) \in
         [-\infty, +\infty)$.
Thus, one can compute the primal-dual gap between primal LCP
\eqref{eq:primal_pb} and dual LCP \eqref{eq:dual_pb} at $(y, p, x, q)$ as
\begin{eqnarray*}
  \begin{split}
  a(y, p) - b(x, q) &= g_1(y, p) - \phi_2(y, p) + g_2(x, q) - \phi_1(x,
  q) \\
  &= \Psi_1(y, p, x, q) +  g_1(y, p) - \phi_2(y, p) + \Psi_2(y, p, x,
  q) + g_2(x, q) - \phi_1(x, q)\\
  &= \hat{\Psi}_1(y, p, x, q) + \hat{\Psi}_2(y, p, x, q) - \phi_1(x,
  q) - \phi_2(y, p)\\
  &= \text{primal-dual gap of GSP}(\Psi_1, \Psi_2,
  g_1, g_2) \text{ at }(y, p, x, q),
  \end{split}
\end{eqnarray*}
where the second equality follows from the fact that $\Psi_1 + \Psi_2
:= 0$.

%% For the dual-gap bound, note that $\forall (x', u', y', v') \in \mathbb{R}^{n_1}_+ \times \mathbb{R}^{l_2} \times \mathbb{R}^{n_2}_+ \times \mathbb{R}^{l_1}$, one has
%% \begin{eqnarray*}
%%   \begin{split}
%%     \underset{x \in \mathbb{R}^{n_1}, u \in \mathbb{R}^{l_2}}{max}\text{ }\begin{bmatrix}x\\u\end{bmatrix}^TK\begin{bmatrix}y'\\v'\end{bmatrix} + g_1(y', v') - g_2(x, u)
%%       &= \underset{x \in \mathbb{R}^{n_1}_+, u \in \mathbb{R}^{l_2}}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + u^T(E_2y' - e_2)\\
%%       &\ge \underset{x \in \mathbb{R}^{n_1}_+}{max}\text{ }x^TAy' - v'^T(E_1x - e_1) + \underset{u \in \mathbb{R}^{l_2}}{max}\text{ }u^T(E_2y' - e_2)\\
%%       &\ge \underset{x \in Q_1}{max}\text{ }x^TAy + \underset{u \in \mathbb{R}^{l_2}}{max}\text{ }u^T(E_2y' - e_2)
%%   \end{split}
%% \end{eqnarray*}

%% and
%% \begin{eqnarray*}
%%   \begin{split}
%%     \underset{y \in \mathbb{R}^{n_2}, v \in \mathbb{R}^{l_1}}{min}\text{ }\begin{bmatrix}x'\\u'\end{bmatrix}^TK\begin{bmatrix}y\\v\end{bmatrix} + g_1(y, v) - g_2(x', u')
%%       &= \underset{y \in \mathbb{R}^{n_2}_+, v \in \mathbb{R}^{l_1}}{min}\text{ }x'^TAy - v^T(E_1x' - e_1) + u'^T(E_2y - e_2)\\
%%       &\le \underset{y \in \mathbb{R}^{n_2}_+}{min}\text{ }x'^TAy + u'^T(E_2y - e_2) - v^T(E_1x' - e_1)
%%   \end{split}
%% \end{eqnarray*}
\end{proof}

@@

\section{The algorithm}
%% According to Theorem \ref{thm:pd}, solving the Nash equilibrium LCPs
%% \eqref{eq:primal_pb}, \eqref{eq:dual_pb} is equivalent to solving the
%% saddle-point problem \eqref{eq:unconstrained_pb}. An attractive method
%% for such a saddle-point problem would be a primal-dual scheme, like
%% that developed in \cite[Algorithm 39]{chambolle2010}. 
%% Usually, to use a primal-dual algorithm, one needs a measure of the
%% ``quality'' of the current iterates as regards being the solution of
%% the saddle-point problem. A natural measure of this fittness is the
%% primal-dual gap, which measures defection from strong-duality.
%% However, the primal-dual gap in \eqref{eq:unconstrained_pb} can be
%% unbounded even at near feasible points.  is well-suited for

Consider the following algorithm
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} - \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, we have the ergodic
error bounds
\begin{eqnarray}
\|\tilde{\epsilon}^{a}_k\| \le \rho\text{ and }\|\tilde{v}^{a}_k\| \le
\epsilon, \forall k \ge 2d_0\|K\|max(5d_0/\rho, 1/\epsilon).
\end{eqnarray}

Thus the iterates $(y^{(k)},p^{(k)},x^{(k)},q^{(k)})$ generated by
Algorithm \ref{Tab:algo} converge ergodically to a
$(\rho,\epsilon)$-Nash Equilibrium for the GSP \eqref{eq:unconstrained_pb}
in no more than $2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ steps.
\end{theorem}
